### 2013-09-23 manuscripts/dpp-msbayes/dpp-msbayes.tex
Starting methods of dpp ms.

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2,3}$ and Mark T.\ Holder$^{2}$

        \bigskip
        $^1$\emph{Biodiversity Institute\\
            $^2$Department of Ecology and Evolutionary Biology\\ 
            University of Kansas\\
            %1345 Jayhawk Blvd\\
            Lawrence, KS 66045\\
            USA}\\[.1in]
        $^3$\emph{Corresponding author} (\href{mailto:joaks1@ku.edu}{\tt
        joaks1@ku.edu})\\

@@

>>>>

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$ and Mark T.\ Holder$^{1}$

        \bigskip
        $^1$\emph{Department of Ecology and Evolutionary Biology,
            % Biodiversity Institute,
            University of Kansas,
            Lawrence, Kansas 66045}\\[.1in]
        $^2$\emph{Corresponding author} (\href{mailto:joaks1@gmail.com}{\tt
        joaks1@gmail.com})\\

@@

\section*{Methods}

\subsection*{The model}
We follow much of the notation of \citet{Oaks2012}, but modify it to
accommodate the new model \ldots

\begin{linenomath}
    Let \npairs{} be the number of pairs of populations, \nloci{i} be the
    number of loci sampled for population pair $i$,
    and \nlociTotal be the total number of unique loci sampled across the
    \npairs{} pairs of populations.
    We use \alignment{i}{j} to represent the multiple sequence alignment of
    locus $j$ for population pair $i$.
    $\alignmentVector = \taxonLocusVector{\alignment}$ is the full dataset,
    i.e., a vector of sequence alignments for all pairs and loci.
    The joint posterior distribution of our model is given by
\begin{equation}
    f(\model{} \given \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{f(\alignmentVector \given \model{}) f(\model{})}{
        f(\alignmentVector)}
    \label{eq:fullModelShort}
    % \begin{split}
    % & f(\geneTreeVector,
    % \numt{},
    % \divtvector, \ancestralThetaVector,
    % \descendantThetaVector{1}, \descendantThetaVector{2},
    % \locusRateHetShapeParameter,
    % \locusMutationRateScalarVector,
    % \bottleTimeVector, \bottleScalarVector{1},
    % \bottleScalarVector{2},
    % \migrationRateVector \given
    % \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    % \mutationRateScalarConstantVector) \\
    % & = \frac{1}{f(\alignmentVector)}
    % f(\numt{}) f(\divtvector \given \numt{})
    % f(\locusRateHetShapeParameter)
    % \Bigg[
    % \prod_{i=1}^{\npairs{}}
    % f(\ancestralTheta{i})
    % f(\descendantTheta{1}{i}, \descendantTheta{2}{i})
    % f(\bottleTime{i})
    % f(\bottleScalar{1}{i}) f(\bottleScalar{2}{i})
    % f(\migrationRate{i}) \\
    % &
    % \prod_{j=1}^{\nloci{i}}
    % f(\alignment{i}{j} \given
    % \geneTree{i}{j}, \hkyModel{i}{j})
    % f(\geneTree{i}{j} \given
    % \divt{i},
    % \ancestralTheta{i}, \descendantTheta{1}{i}, \descendantTheta{2}{i},
    % \ploidyScalar{i}{j}, \mutationRateScalarConstant{i}{j},
    % \locusMutationRateScalar{j},
    % \bottleTime{i}, \bottleScalar{1}{i}, \bottleScalar{2}{i},
    % \migrationRate{i})
    % \Bigg]
    % \Bigg[
    % \prod_{j=1}^{\nlociTotal}
    % f(\locusMutationRateScalar{j} \given \locusRateHetShapeParameter)
    % \Bigg],
    % \label{eq:fullmodel}
    % \end{split}
\end{equation}
where \hkyModelVector, \ploidyScalarVector, and \mutationRateScalarConstantVector
are vectors of fixed parameters specified by the user.
More specifically $\hkyModelVector = \taxonLocusVector{\hkyModelVector}$ is a
vector of fixed \hky model parameters for each alignment.
% where $\geneTreeVector = \taxonLocusVector{\geneTree}$ are the gene trees upon
% which each \alignment{i}{j} evolved according to the \hky substitution model
% parameters \hkyModel{i}{j}.
% The \hky model parameters for each alignment reside in vector 
% $\hkyModelVector = \taxonLocusVector{\hkyModel}$,
% and are fixed constants provided by the user.
% \divtvector is the vector of times, in coalescent units, when the populations
% of each pair diverged, \taxonVector{\divt}.
% \numt{} is the hyper-parameter controlling the number of unique \divt{} within
% \divtvector.
% $\ancestralThetaVector = \taxonVector{\ancestralTheta}$ is the vector of
% \myTheta{} parameters for the ancestral population of each population pair.
% $\descendantThetaVector{1} = \taxonVector{\descendantTheta{1}}$ is the vector of
% \myTheta{} parameters for the $1^{st}$ descendant population of each
% pair;
% $\descendantThetaVector{2} = \taxonVector{\descendantTheta{2}}$ is the same for
% the $2^{nd}$ descendant population of each pair.
% $\ploidyScalarVector = \taxonLocusVector{\ploidyScalar}$ and
% $\mutationRateScalarConstantVector = \taxonLocusVector{\mutationRateScalarConstant}$
% are vectors of \myTheta{}-scaling constants provided by the user
% (Table~\ref{tab:notation}).
% Furthermore, there are locus-specific \myTheta{}-scaling
% parameters in the vector $\locusMutationRateScalarVector =
% \locusVector{\locusMutationRateScalar}$.
% \locusRateHetShapeParameter is the shape parameter of the gamma prior
% distribution on each \locusMutationRateScalar{}.
% $\bottleScalarVector{1} = \taxonVector{\bottleScalar{1}}$ is the vector of
% \myTheta{}-scaling parameters that determine the magnitude of the bottleneck in
% the $1^{st}$ descendant population of each population pair,
% whereas $\bottleScalarVector{2} = \taxonVector{\bottleScalar{2}}$ is the same
% for the $2^{nd}$ descendant population of each pair;
% for both descendants of each population pair, the bottleneck begins immediately
% after divergence in forward-time.
% $\bottleTimeVector = \taxonVector{\bottleTime}$ is the vector of the
% proportions of time between present and \divt{} when the bottleneck ends for
% both populations in each pair; after which the populations grow exponentially to
% present.
% $\migrationRateVector = \taxonVector{\migrationRate}$ is the vector of
% symmetric migration rates between the descendant populations of each pair.
\end{linenomath}
